\large COOPERATIVE 3-D MAP GENERATION USING MULTIPLE UAVS

### 2015-05-15 draft.tex
Fleshed out multiple robot section.

\section{Online Mapping}
\noindent As discussed in the overview, each quadcopter needs to send its map over the network to be fused together. There are two primary methods to solve this, both with unique drawbacks. One such method is to deliver the entire aggregated point cloud map at given intervals to the server - this is immediately unfeasible because as time grows, the size of the map will grow to hundreds of megabytes and current network speeds are unable to process such a load in a reasonable time frame. The other solution is to send each individual point cloud corresponding to a timestep over the network, resulting in a reconstruction of the map on the server. This is inefficient, because the map has already been built onboard and it is redundant to perform the same operation remotely. The experiments in this report used the latter method despite its obvious weaknesses - it was the best choice given the constraints and time restrictions of the project.

Coupled with the mapping component of the RGBDSLAM_V2 package, a custom ROS node was written (integrated with RGBDSLAM_V2) that provided a stream of clouds added to the map, each corresponding to a new node added within the graph. As shown in figure X, these clouds are sent over the network and simultaneously received by a server or other external computer. For each cloud, the external computer also looks up the corresponding transformation between the fixed reference frame for the map and the current camera pose by listening to the transformation broadcaster within the RGBDSLAM_V2 algorithm. Once this transformation is received, it is applied to the new cloud, which is then concatentated to the current map.

% Networked map building algorithm flowchart
\begin{figure}[h]
 \caption{Live test of a single quadcopter.}
 \centering
   \includegraphics[width=0.8\textwidth]{images/single_test}
\end{figure}

\section{Map Fusion}
\noindent When transitioning from one robotic agent generating a global 3-D map to multiple robot agents, an algorithm capable of fusing each robot's local map together is essential. Each map generated by an individual robot has its own point cloud and pose (or transformation) in 3-D space. In order to make sense of these individual clouds, the algorithm accomplishes two goals: 1) it transforms two maps into the same global reference frame, 2) stitches the maps together and 3) eliminates redundant data points. By incrementally inputting maps into the algorithm, the server can output a final 3-D representative of all robotic agents' mapping efforts. As shown in Figure 2, this algorithm is divided into two key sections and follows a similar approach to Henry et. al.\cite{henry2012rgb}.

% Map fusion algorithm flowchart
\begin{figure}[h]
 \caption{Data flow of map fusion algorithm.}
 \centering
   \includegraphics[width=0.9\textwidth]{images/mapfusion}
\end{figure}

@@

    \noindent Given two maps within their own reference frame, it's necessary to transform the source map into the reference frame of the target map. The point clouds are first put through an initial alignment phase using the Sample Concensus Initial Alignment algorithm \cite{rusu2009fast}. This outputs a final transformation which is applied to the source cloud. In laymen's terms, this basically provides a large correction to the initial alignment of the two clouds, seen in Figure ~\ref{fig:Raw concatentation.}.

@@

    \noindent Within the alignment process itself, there are several subprocesses. First, the normals $N_{source}$ and $N_{target}$ are found by PCL's normal estimator. These normal clouds are then used in PCL's Fast Point Feature Histogram (FPFH) \cite{rusu2009fast,rusu2009fastlabel} estimator, to generate approximate feature clouds $F_{source}$ and $F_{target}$. Lastly, these feature clouds from this process are used to estimate an initial transformation $T$, which is applied to the initial source cloud to obtain an initial alignment. This gives the clouds a reasonably close placement relative to each other, and allowing optimal usage of ICP in order to fine tune them.

@@

Due to financial and logistical difficulties, a test involving two quadcopters flying simultaneously in real time was unable to be conducted within the time frame for this project. As an alternative to demonstrate effectiveness of this approach, two separate flights using the same quadcopter were conducted in the same environment and saved into ROS bags. These ROS bags were then simulated as live nodes, with map data streaming at the same frequency and conditions as a real multi-robot flight test - this provided data to the map fusion server that exactly duplicates two quadcopters flying simultaneously and was an acceptable substitution for a real test.

@@

As stated earlier, this project did not focus on navigation or control of multiple quadcopters and took an interest purely within the feasibility of mapping using multiple quadcopters. A natural progression forward would be to implement localization and possible object avoidance. The RGBDSLAM algorithm was used exclusively for its mapping and pose graph features, but is also capable of estimating trajectory and facilitating autonomous navigation.

>>>>

When transitioning from one robotic agent creating its own map to generating a global 3-D map for multiple disjoint robot agents, it's essential to fuse each robot's maps together. This requires the introduction of a centralized, external server as the onboard computational units do not have the computing power to both generate the map for singular robot usage and to construct the cooperative map simultaneously in the case of multiple agents. The server's function is underlined by two key algorithms, first the \textsl{Online Mapping} algorithm which reconstructs each robot's map in real time as it sends timestamped point clouds over the network and second the \textsl{Map Fusion} algorithm, which fuses the the two aggregate disjoint maps together.

\section{Online Mapping}
As discussed in the overview, each quadcopter produces a point cloud segment which it sends over the network to be aggregated into a single map corresponding to that robotic agent. There are two primary methods to accomplish this, both with unique drawbacks. The first method is to deliver the entire aggregated point cloud map computed by RGBDSLAM at given intervals to the server - this becomes infeasible very quickly because as time grows, the size of the map will grow to hundreds of megabytes and current network speeds are unable to process such a load in a reasonable time frame. The other solution is to send each individual point cloud corresponding to a timestep over the network, resulting in a reconstruction of the map on the server. This is inefficient, because the map has already been built onboard and it is redundant to perform the same operation remotely. The experiments in this report used the latter method (despite its obvious weaknesses) given constraints and time restrictions of the project.

% Networked map building algorithm flowchart
\begin{figure}[h!]
 \caption{Data flow of online mapping algorithm.}
 \centering
   \includegraphics[width=0.8\textwidth]{images/online_streaming}
 \label{fig: online stream.}
\end{figure}

Coupled with the mapping component of the RGBDSLAM package, a custom ROS node was written (integrated with RGBDSLAM) that provided a stream of clouds added to the map to through a new ROS topic, each corresponding to new nodes added within the graph. As shown in \ref{fig: online stream.}, these clouds and their respective transforms\footnote{The transform of the cloud is that between the RGB optical frame of the Kinect camera and the fixed frame of the robot's map.} are computed by RGBDSLAM, sent procedurally over the network, received by a server or other external computer, which then executes the online map builder algorithm for each cloud. The algorithm first matches the new cloud $\bf{P_n}$ with its transform $\bf{T_n}$ by performing a transformation lookup keyed by the timestamp $\bf{t_n}$ of the cloud (located in its header data). Once located, the transformation is applied to the cloud, changing its pose to be relative to the aggregate map $\bf{P_a}$. Once this transformation is applied, the new cloud can be simply appended to the current aggregate cloud in the simple operation $\bf{P_a} += \bf{P_n}$  - this new version of the cloud $\bf{P_a}$ is then saved into a database or filesystem.

\section{Map Fusion}
\noindent Once these aggregate maps corresponding to the robotic agents are reconstructed on the server, each map has its own point cloud and transformation in 3-D space. Unlike the \textsl{Online Mapping} algorithm, there is not a known transformation\footnote{In Online Mapping, the fixed frame is determined by the pose of the first cloud generated, so a transformation can be found from the camera frame of subsequent maps. In Map Fusion, no such initial transformation is known.} between the frames of the disjoint maps - this means the \textsl{Map Fusion} procedure must approximate the transformation between the two maps. Following a similar approach to Henry et. al.\cite{henry2012rgb}, the algorithm transforms two maps into the same global reference frame through several alignment approximations, stitches the maps together, and eliminates redundant data points by applying a voxel filtering algorithm. By incrementally applying the map fusion algorithm to the aggregate maps, the server outputs a timestamped representation of the global map. As shown in Figure 2, this algorithm is divided into two key sections.

% Map fusion algorithm flowchart
\begin{figure}[h!]
 \caption{Data flow of map fusion algorithm.}
 \centering
   \includegraphics[width=0.9\textwidth]{images/mapfusion}
 \label{fig: map fusion.}
\end{figure}

@@

    \noindent As mentioned in the overview, it's necessary to transform the source map into the reference frame of the target map, however, this process must be approximated through an iterative process. The point clouds are first put through an initial alignment phase that provides a rougher, larger-scale transformation estimation. This is done using the Sample Concensus Initial Alignment algorithm \cite{rusu2009fast}. from the Point Cloud Library. This process outputs a final transformation which is applied to the source cloud, as seen in Figure ~\ref{fig:Raw concatentation.}.

@@

    \noindent Within the alignment process itself, there are several subprocesses. First, the normals $N_{source}$ and $N_{target}$ are found by PCL's normal estimator. These normal clouds are then used in PCL's Fast Point Feature Histogram (FPFH) \cite{rusu2009fast,rusu2009fastlabel} estimator, to generate approximate feature clouds $F_{source}$ and $F_{target}$. These feature clouds store feature descriptors for each point in the cloud, in this case, FPFH features. Although, the theory behind image features is beyond the scope of this report, the FPFH feature approximates the mean curvature of a point's k-neighbors' geometry with a histogram of values - this type of feature allows computation of a feature cloud in asympototically linear time, giving a powerful but relatively quick feature estimator. Lastly, these feature clouds from this process are used to estimate an initial transformation $T$, which is applied to the initial source cloud to obtain an initial alignment. This gives the clouds a reasonably close placement relative to each other, and allowing optimal usage of ICP in order to fine tune them.

@@

Due to financial and logistical difficulties, a test involving two quadcopters flying simultaneously in real time was unable to be conducted within the time frame for this project. As an alternative to demonstrate effectiveness of the approaches demonstrated in this report, two separate flights using the same quadcopter were conducted in the same environment and saved into ROS bags. These ROS bags were then simulated as live agents, with map data streaming at the same frequency and conditions as a real multi-robot flight test - this provided data to the map fusion server that exactly duplicates two quadcopters flying simultaneously and serves as an acceptable substitution for a real test.

A test was conducted in the L.I.N.K.S Lab, with a simple spinning motion to capture the depth and RGB data of the room. One half of the room was captured by the first robot and the second half of the room was captured by a second robot.

@@

As stated earlier, this project did not focus on navigation or control of multiple quadcopters and focused on the feasibility of mapping using multiple quadcopters. A natural progression forward would be to implement localization and possibly object avoidance algorithms in parallel with the mapping procedures. The RGBDSLAM algorithm in this report was used exclusively for its mapping and pose graph features, but was selected partly because of its capabilities of estimating trajectory and facilitating full autonomous navigation. Implementation of navigation in tandem with the concepts presented in this report would be a significant achievement.

In an optimal world, a centralized approach to cooperative mapping will not be necessary and the onboard computational units could cooperatively compute the global map, independent of external communication. It's clear that the application of such a concept is limited largely by technological capabilities. A possible solution to this problem could be to add a secondary computational unit aboard each robotic agent - this would allow for sufficient computational overhead to compute the global map in a decentralized manner, but would increase the power and weight requirements of the robot significantly, resulting in need of a larger capacity battery to compensate for increased thrust and power needs. This would, in turn, increase the weight of the quadcopter and reduce flight time.
